RAX: A porting complexity evaluation tool for RISC-V

### 2024-01-29 Paper/latex2/paper.tex
update

\usepackage{multirow}
\usepackage{svg}
\usepackage{xcolor}

@@

Based on the analysis of previous evaluation tools, we selected factors with the greatest potential and that can be extracted through automated methods to define Arch\_code.
Arch\_code includes assembly code, conditional compilation and macro structure, Intrinsic functions, Builtin functions, architecture-related build scripts, and system calls.
We use an automated architecture binding code scanning tool to obtain statistics on the number of lines and frequencies of Arch\_code.

@@

\begin{table}
  \caption{Tool factors comparison}
  \label{tab:Tool}
  \begin{tabular}{ccccccc}
    \toprule
    & Asm & Intrinsic & Builtin & Conditional compilation and macro & Buildscripts & CC \\
    \midrule
    Toolone & 1 & 1 & 1 & 1 & 1 & 0\\
    RAX & 1 & 1 & 1 & 1 & 1 & 1 \\
  \bottomrule
\end{tabular}
\end{table}

>>>>

\usepackage{multirow}
\usepackage{svg}
\usepackage{xcolor}
\usepackage{bbding}

@@

Based on the analysis of previous evaluation tools, we selected factors with the greatest potential and that can be extracted through automated methods to define Arch\_code.
Arch\_code includes assembly code, conditional compilation and macro(ccm) structure, Intrinsic functions, Builtin functions, architecture-related build scripts, and system calls.
We use an automated architecture binding code scanning tool to obtain statistics on the number of lines and frequencies of Arch\_code.

@@

\begin{table}
   \caption{Tool factors comparison}
   \resizebox{0.5\textwidth}{!}{
  \label{tab:Tool}
  \begin{tabular}{ccccccc}
    \toprule
    & Asm & Intrinsic & Builtin & CCM & Buildscripts & CC \\
    \midrule
    Toolone & \Checkmark & \Checkmark  & \Checkmark  & \Checkmark  &\Checkmark  & \XSolid\\
    RAX & \Checkmark  & \Checkmark  & \Checkmark  & \Checkmark  & \Checkmark & \Checkmark  \\
  \bottomrule
\end{tabular}
}
\end{table}
